---
title: "AUS RAIN DATA"
output: html_notebook
---

# Installs n Imports
```{r}
install.packages("pROC")
install.packages("car")
install.packages("caTools")
install.packages("tidyverse")
library(pROC)
library(car)
library(caTools)
library(ggplot2)
library(plotly)
library(tidyverse)
install.packages("corrplot")
library(corrplot)
install.packages(c("rpart", "rpart.plot", "e1071", "randomForest", "AppliedPredictiveModeling", "caret", "ROCR"))
library(rpart) #This one is for building decision trees
library(rpart.plot)
library(e1071)
library(randomForest)
library(ROCR)
library(caret)
```



# Make it rain

```{r}
ausdata <- read.csv("weatherAUS.csv")
head(ausdata)
```

# Sumarry

```{r}
summary(ausdata)
```

# Column names

```{r}
colnames(ausdata)
```

# Initial observations with predicitions

Multiple columns can be used to predict things and determine things.

Big hint was weather there would be RainTomorrow.. and how accurate this would be.


Meant to use Classifcation

Personal Note - DO NOT LOOK at CORRELATION


Initial Prediction =

Looking at trends later..
Initial to look at this in better light. 
1. Brisbane has faster wind than the rest of austrailia

Expand this further
2. Comparison between rainToday and rainTomorrow 

3. Decision Trees to determine how reliable RainTomorrow would be.

RainTomorrow = Boolean. Yes No
look how it is done on Classification module for R.. 

# inital play

Initial plot
```{r}
qplot(x = ausdata$Date , y = ausdata$WindGustSpeed, col = ausdata$Location)
```

```{r}
qplot(x = ausdata$Date , y = ausdata$WindGustSpeed)
```
add a line.. 


```{r}
cols <- colnames(ausdata)
```



Get rid of the nulls
```{r}
ausdfnoNA <- na.omit(ausdata)
```

DropNa(RF, var=c("dede")) - drop column

data$dowmdomw[column = value]<- NULL

data <- data[condition]

# 1. Brisbane has faster wind than the rest of austrailia

Using Excel the highest speed in Brisbane is 93

Fasted wind in each location 

```{r}
max(ausdata$WindGustSpeed, na.rm = TRUE)
```

```{r}
max(ausdata$Location == "Brisbane", ausdata$WindGustSpeed, na.rm = TRUE)
```

dataBris <- ausdata[ausdata$Location == "Brisbane"]

```{r}
dataBris <- ausdata$Location == "Brisbane"
```

```{r}
summary(dataBris)
```




# 3. Decision Trees to determine how reliable RainTomorrow would be

```{r}
head(ausdata)
str(ausdata)
summary(ausdata)
head(ausdata)
tail(ausdata)
```

Data Clean For what we need.

2 rounds of Data clean..

round 1 & 2 Clean set of RainToday

```{r}
data1aus <- ausdata[complete.cases(ausdata$RainToday),]
dataRTRT <- data1aus[complete.cases(data1aus$RainTomorrow),]
```


Plot what results based on country, based on data and RainToday:

```{r}
qplot(x = dataRTRT$Date, y = dataRTRT$RainToday, col = dataRTRT$Location)
```

Was a mistake.. BUT there is no presence of N/A's

Plot what results based on country, based on data and RainTomorrow:

```{r}
qplot(x = dataRTRT$Date, y = dataRTRT$RainTomorrow, col = dataRTRT$Location)
```

All HOPE lost...
CHEAT... we need no NA's data without Null's..

```{r}
dataDD <-  na.omit(dataRTRT) 
head(dataDD)
```

Create train, test data from the data (de Nulled)

```{r}
set.seed(123)
sample <- sample.split(dataDD,SplitRatio = 0.75)
train <- subset(dataDD, sample==TRUE) 
test  <- subset(dataDD, sample==FALSE)
```

Specify variables/columns which I thought would affect the weather.. and create a decision tree based on that.
```{r}
fit <-  rpart(RainToday ~ Location + MinTemp + MaxTemp +Temp9am+Humidity9am+Pressure9am+Cloud9am+ Evaporation + Sunshine,
              method = "class",
              data = dataDD,
              control =rpart.control(minsplit = 1, depth= 5),
              parms= list(split ="information"))
```

Plot the decision tree..

```{r}
rpart.plot(fit, type=5, extra=2)
```

Perform a prediction 

```{r}
predict(fit, test)
```

Remove RainToday so that i can test.
```{r}
dataDDT <- dataDD 
dataDD$RainToday <- NULL
```

Perform another prediction and produce a matrix:
```{r}
Predict_dd <-  predict(object=fit,
                        newdata= test,
                        type="class")

confusionMatrix(data=Predict_dd, reference= test$RainToday)
```



predictdd 

compare id by id by test data and check value.


calculation is CORRECT

test$RainTomorrow Predict_dd YES/NO

```{r}
score <- 0
for (i in 1:nrow(test)){
  if (test$RainTomorrow[i] == Predict_dd[i]) {
    score <- score+1
  }
}
(score / nrow(test))*100
```

TUNE it..

